\documentclass[12pt,a4paper]{article}
\usepackage{times,url,hyperref}

\topmargin=-0.5in
\oddsidemargin=0in
\evensidemargin=0in
\textwidth=6.5in
\textheight=9.5in

\title{mod2sbml.py, Version 3.1.1.1 --- an SBML-shorthand to SBML
translation tool}
\author{\href{https://darrenjw.github.io/}{Darren J
Wilkinson}\\
email: \href{mailto:darren.j.wilkinson@durham.ac.uk}{\texttt{darren.j.wilkinson@durham.ac.uk}}}
\date{\today}

\begin{document}
\sf
\maketitle

\section{Introduction}

This document describes a reference implementation of a SBML-shorthand
to SBML compiler: \verb$mod2sbml.py$, written in Python. It can be
used either as a simple command-line translator, or by Python
programmers as a Python module. The module requires libSBML version
$\geq$ 4.1.0 (and $<$ 5.0.0)
and the libSBML python bindings. Please ensure that these are installed and
working before attempting to use this software. Note that the libSBML
API is currently undergoing a period of rapid change, and so it really
does matter which version of libSBML you have installed.

SBML-shorthand is described in a separate specification document.

There is also a reference implementation of a SBML
to SBML-shorthand translator (\verb$sbml2mod.py$)
available from the
SBML-shorthand web site. This works (almost) exactly like \verb$mod2sbml$
except that the conversion is in the other direction. This document
therefore serves as documentation for that script too (but see the
\verb$__doc__$ strings for further info).

\section{Version}

mod2sbml.py has a version number of the form $a.b.c.d$ where $a.b.c$
corresponds to the version number of SBML-shorthand that the software
targets, and $d$ is the version of the software for that
SBML-shorthand version. So, version 3.1.1.1 is the first version of
the software aimed at SBML-shorthand version 3.1.1.

\section{Command-line filter}

Suppose that a SBML-shorthand model is contained in a file called
\verb$mymodel.mod$ in the current directory. Then either of the commands
\begin{verbatim}
% mod2sbml.py < mymodel.mod > mymodel.xml
% mod2sbml.py mymodel.mod > mymodel.xml
\end{verbatim}
will result in the production of the SBML \verb$mymodel.xml$
corresponding to the shorthand description in \verb$mymodel.mod$. This
obviously requires that \verb$mod2sbml.py$ is executable and in the
current path. If you don't know what that means, putting the
\verb$mod2sbml.py$ file in the current directory and typing
\begin{verbatim}
% python mod2sbml.py mymodel.mod > mymodel.xml
\end{verbatim}
should still work.

\section{Python module}

Python programmers can also use this module directly from python. A
couple of example sessions are given below.
First, an example using file streams.
\begin{verbatim}
>>> from mod2sbml import Parser
>>> p=Parser()
>>> inS=open("mm.mod","r")
>>> d=p.parseStream(inS)
>>> print d.getModel()
>>> print d.toSBML()
\end{verbatim}
Next, an example using strings.
\begin{verbatim}
>>> from mod2sbml import Parser
>>> p=Parser()
>>> s=open("mm.mod","r").read()
>>> d=p.parse(s)
>>> print d.toSBML()
\end{verbatim}
The returned \verb$libsbml$ object, \verb$d$, is a libSBML
document. The module raises the exception \texttt{ParseError} if it 
encounters a fatal error during parsing.

Note that Python \verb$__doc__$ strings are provided for the module, the Parser class, and the
two public methods of the Parser class. For further details, see the
source code...

\section{Links}

\begin{tabular}{rl}
SBML-shorthand & {\small
\href{http://www.staff.ncl.ac.uk/d.j.wilkinson/software/sbml-sh/}{\url{www.staff.ncl.ac.uk/d.j.wilkinson/software/sbml-sh/}}
}\\
SBML & \href{http://sbml.org/}{\url{sbml.org}} \\
Python & \href{http://www.python.org/}{\url{www.python.org}}
\end{tabular}



\end{document}
